Articles Of Association

### 2014-11-17 Articles_of_Association_Melbourne_Bitcoin_Technology_Centre_MBTC_2015.tex
fix grammer in the purpose

      \item The purposes of the incorporated association is to promote and assist the adoption and growth of the Bitcoin trading economy and support businesses and consumers embrace digital currency and related technologies and assist our membership to work on building the future of money.

>>>>

      \item The purposes of the incorporated association is to promote and assist the adoption and growth of the Bitcoin trading economy and support businesses and consumers embrace digital currency and related technologies and assist our members work on building the future of money.
